### 2016-10-05 robust-software.tex
Bolding a few subpoints

Installing or running a program with root privileges is often
convenient, since doing so automatically bypasses all those pesky safety
checks that might otherwise get in the user's way. However, those checks
are there for a reason: scientific software packages may not
intentionally be malware, but one small bug or over-eager file-matching
expression can certainly make them behave as if they were. Outside of
very unusual circumstances, packages should therefore not require root
privileges to set up or use.

@@

Developers should therefore allow packages to be installed in an
arbitrary location, e.g., under a user's home directory in
\texttt{\textasciitilde{}/packagename}, or in directories with standard
names like \texttt{bin}, \texttt{lib}, and \texttt{man} under a chosen
directory. If the first option is chosen, the user may need to modify
her search path to include the package's executables and libraries, but
this can (more or less) be automated, and is much less risky than
setting things up as root.

@@

For these reasons, users should be able to set the names and locations
of input and output files as command-line parameters. This rule applies
to reference data sets as well as the user's own data: if a user wants
to try a new gene identification algorithm using a different set of
genes as a training set, she should not have to edit the software to do
so.

A corollary to this rule is that a package should not require users to
navigate to a particular directory to do their work. ``Where I have to
be'' is just another hard-coded path.

>>>>

Installing or running a program with root privileges is often
convenient, since doing so automatically bypasses all those pesky safety
checks that might otherwise get in the user's way. However, those checks
are there for a reason: scientific software packages may not
intentionally be malware, but one small bug or over-eager file-matching
expression can certainly make them behave as if they were. Outside of
very unusual circumstances,
\textbf{packages should not require root privileges to set up or use}.

@@

Developers should therefore
\textbf{allow packages to be installed in an arbitrary location},
e.g., under a user's home directory in
\texttt{\textasciitilde{}/packagename}, or in directories with standard
names like \texttt{bin}, \texttt{lib}, and \texttt{man} under a chosen
directory. If the first option is chosen, the user may need to modify
her search path to include the package's executables and libraries, but
this can (more or less) be automated, and is much less risky than
setting things up as root.

@@

For these reasons, users should be able to
\textbf{set the names and locations of input and output files as command-line parameters}.
This rule applies to reference data sets as well as the user's own
data: if a user wants to try a new gene identification algorithm using
a different set of genes as a training set, she should not have to
edit the software to do so.

A corollary to this rule is
\textbf{do not require users to navigate to a particular directory to do their work}.
``Where I have to be'' is just another hard-coded path.
